Modelling the Lymphatic Metastatic Progression Pathways of OPSCC from Multi-Institutional Datasets

### 2023-08-11 src/tex/ms.tex
[showyourwork] overleaf sync

\newcommand{\ju}[1]{{\textcolor{red}{#1}}}

@@

The most likely model parameters for the winning graph, corresponding to the mean of the marginals of the sampled posterior distributions, are given by \ju{as placeholder taken from figure 7.5 of your thesis}: $b_1=?$, $b_2=0.37$, $b_3=0.07$, $b_4=0.01$, $b_5=?$, $b_7=0.02$ for the base probabilities, and $t_{23}=0.13$, $t_{34}=0.14$, $t_{21}=?$, $t_{25}=?$, $t_{35}=?$, and $p_{late}=0.4$ for the time prior parameter for advanced T-category patients (where we have fixed $p_{early}=0.3$ for early T-category tumors, and $t_{max}=10$ time steps). The result that $t_{23}$ and $t_{34}$ are relatively large compared to $b_3$ and $b_4$ reflects the observation that skip metastases in levels III and IV without involvement of the upstream level is rare. Since level II has no parent nodes except for the primary tumor, $b_2$ can be easily related to the prevalence of involvement in level II. The probability for no involvement of level II when the patient is diagnosed after $t$ time steps is $\left(1-b_2\right)^t$. The prevalence of level II involvement for late T-category patients is thus $1-\sum_{t=0}^{10} \left(1-0.37\right)^t 0.4^t \, (1-0.4)^{(10-t)}\binom{10}{t}\approx 0.8$, which agrees with \cref{fig:bg_prevalences}.

@@

\begin{figure}
    \script{wg_sens_spec_risks.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/wg_sens_spec_risks.png}
        \caption{Dependence of risk of occult disease on sensitivity and specificity. The figure shows the mean risk (i.e. averaged over the risk calculated for different model parameter samples \ju{is that what you do?}) in level IV in patients with clinical involvement of levels II and III.}
        \label{fig:wg_sens_spec_risks}
    \end{centering}
\end{figure}

>>>>

\newcommand{\ju}[1]{{\textcolor{red}{#1}}}
\newcommand{\rl}[1]{{\textcolor{blue}{#1}}}

@@

The most likely model parameters for the winning graph, corresponding to the mean of the marginals of the sampled posterior distributions, are given by: $b_1=\variable{output/wg_mean_b1.txt}\%$, $b_2=\variable{output/wg_mean_b2.txt}\%$, $b_3=\variable{output/wg_mean_b3.txt}\%$, $b_4=\variable{output/wg_mean_b4.txt}\%$, $b_5=\variable{output/wg_mean_b5.txt}\%$, $b_7=\variable{output/wg_mean_b7.txt}\%$ for the base probabilities, and $t_{23}=\variable{output/wg_mean_t23.txt}\%$, $t_{34}=\variable{output/wg_mean_t34.txt}\%$, $t_{21}=\variable{output/wg_mean_t21.txt}\%$, $t_{25}=\variable{output/wg_mean_t25.txt}\%$, $t_{35}=\variable{output/wg_mean_t35.txt}\%$, and $p_\text{late}=\variable{output/wg_mean_late_p.txt}\%$ for the time prior parameter for advanced T-category patients (where we have fixed $p_{early}=0.3$ for early T-category tumors, and $t_{max}=10$ time steps). The result that $t_{23}$ and $t_{34}$ are relatively large compared to $b_3$ and $b_4$ reflects the observation that skip metastases in levels III and IV without involvement of the upstream level is rare. Since level II has no parent nodes except for the primary tumor, $b_2$ can be easily related to the prevalence of involvement in level II. The probability for no involvement of level II when the patient is diagnosed after $t$ time steps is $\left(1-b_2\right)^t$. The prevalence of level II involvement for late T-category patients is thus $1-\sum_{t=0}^{10} \left(1-0.37\right)^t 0.4^t \, (1-0.4)^{(10-t)}\binom{10}{t}\approx 0.8$, which agrees with \cref{fig:bg_prevalences}.

@@

\begin{figure}
    \script{wg_sens_spec_risks.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/wg_sens_spec_risks.png}
        \caption{Dependence of risk of occult disease on sensitivity and specificity. The figure shows the risk of involvement in level IV, given the mean of the parameter samples, drawn during sampling, in patients with clinical involvement of levels II and III.}
        \label{fig:wg_sens_spec_risks}
    \end{centering}
\end{figure}
